---
title: "Lab 3"
author: "[Mack and Jill]"
date: "[10/2/2017]"
output:
  html_document:
    fig_height: 4
    fig_width: 6
---

**Author:** [Mackenzie O'Brien]

**Discussants:** [Jillian Preece]

* * *

**Load Kobe's data:**
```{r}
load(url("http://foxweb.marist.edu/users/duy.nguyen2/kobe.RData"))
head(kobe)

kobe$basket[1:9]
```

* * *

#### Exercise 1: 
A streak of length 1 means that he, for example, made the one basket in a row and then missed the next. A streak of length 0 means that he missed the basket and did not have a hit.
```{r}
kobe_streak<-calc_streak(kobe$basket)
barplot(table(kobe_streak))
```


#### Exercise 2:
Based on the barplot, Kobe had a lot of misses (streaks of length 0), and seemed to make a lot of baskets once and then miss the next. He did not seems to make a lot in a row, typically his streak length was 0 or 1, with his longest streak being 4 in a row.
```{r}
outcomes<-c("heads","tails")
sample(outcomes,size = 1,replace = TRUE)
sim_fair_coin<-sample(outcomes,size = 100,replace = TRUE)
sim_fair_coin
table(sim_fair_coin)

```

#### Exercise 3:
In our simulation of the unfair coin,heads only came up 17 times, while tails appeared 83 times.
```{r}
set.seed(1)
sim_unfair_coin<-sample(outcomes,size = 100,replace = TRUE, prob=c(0.2,0.8))
sim_unfair_coin
table(sim_unfair_coin)
```


#### Exercise 4:
To make the shooter simulation match Kobe, the hit probability must be set to 45% and the miss probability to 55%. 
```{r}
outcomes<-c("H","M")
sim_basket<-sample(outcomes,size = 1,replace = TRUE)
?sample
sim_basket<-sample(outcomes,size=133,replace=TRUE,prob=c(0.45,0.55))
sim_basket
kobe$basket
```


* * *
### On your own:
```{r}
#streak lengths of sim_basket
sim_streak<-calc_streak(sim_basket)
sim_streak
barplot(table(sim_streak))
```


#### 1:


#### 2:


#### 3:


#### 4:


