---
title: "Lab 7"
author: "[Team Mack and Jill]"
date: "[11/16/2017]"
output:
  html_document:
    fig_height: 4
    fig_width: 6
---

**Author:** [Mack]

**Discussants:** [Jill]

* * *

**Load data:**
```{r}
load(url("http://foxweb.marist.edu/users/duy.nguyen2/atheism.RData"))
head(atheism)
```

* * *

#### 1:
We think that the findings are sample statistics, because only 50,000 people were surveyed globally, yet the population of the world is around 7.6 billion.
#### 2:
Each row of table 6 corresponds to a different countries' polled religious beliefs, displaying the percentages based on the sample of religious, non religious, and atheists.
Each row of atheism corresponds to an individual answer of the poll, giving that person's country, religious viwes, and the year in which they were surveyed.
#### 3: 
Yes, the proportion matches up with Tabl6 at 5%.
```{r}
us12 <- subset(atheism, nationality == "United States" & year == "2012")
head(us12)
summary(us12)
proportion=50/(952+50)
proportion
```

#### 4:
The conditions that need to be met for a confidence interval are: the sample is simple and random, the sampling distribution is approximately normal or n>=40, and the population standard deviation is unknown. The sample from us12 is random, n>40, and we do not know the standard deviation.
```{r}
load(url("http://foxweb.marist.edu/users/duy.nguyen2/inference.RData"))
inference(us12$response, est = "proportion", type = "ci", method = "theoretical", success = "atheist")

```


#### 5:
me <- 2 * sqrt(p * (1 - p)/n)

```{r}
meUS<- 2 * sqrt(0.0499 * (1 - 0.0499)/1002)
meUS
```
#### 6:
```{r}
brazil02 <- subset(atheism, nationality == "Brazil" & year == "2012")
inference(brazil02$response, est = "proportion", type = "ci", method = "theoretical", success = "atheist")
meB <- 2 * sqrt(0.01 * (1 - 0.01/2002))

france02<-subset(atheism, nationality == "France" & year == "2012")
inference(france02$response, est = "proportion", type = "ci", method = "theoretical", success = "atheist")
meF <- 2 * sqrt(0.2873 * (1 - 0.2873)/1688)
```

#### 7:
The closer the population proportion is to .5, the larger it is, while the closer to 1.0 or 0.0, the smaller it is.
```{r}
n <- 1000
p <- seq(0, 1, 0.01)
me <- 2 * sqrt(p * (1 - p)/n)
plot(me ~ p, ylab = "Margin of Error", xlab = "Population Proportion")
```

#### 8:
```{r}
p <- 0.1
n <- 1040
p_hats <- rep(0, 5000)

for(i in 1:5000){
  samp <- sample(c("atheist", "non_atheist"), n, replace = TRUE, prob = c(p, 1-p))
  p_hats[i] <- sum(samp == "atheist")/n
}

hist(p_hats, main = "p = 0.1, n = 1040", xlim = c(0, 0.18))
```

#### 9:
```{r}
p <- 0.1
n <- 400
p_hats <- rep(0, 5000)

for(i in 1:5000){
  samp <- sample(c("atheist", "non_atheist"), n, replace = TRUE, prob = c(p, 1-p))
  p_hats[i] <- sum(samp == "atheist")/n
}

hist(p_hats, main = "p = 0.1, n = 400", xlim = c(0, 0.18))


p <- 0.02
n <- 1040
p_hats <- rep(0, 5000)

for(i in 1:5000){
  samp <- sample(c("atheist", "non_atheist"), n, replace = TRUE, prob = c(p, 1-p))
  p_hats[i] <- sum(samp == "atheist")/n
}

hist(p_hats, main = "p = 0.02, n = 1040", xlim = c(0, 0.18))

p <- 0.02
n <- 400
p_hats <- rep(0, 5000)

for(i in 1:5000){
  samp <- sample(c("atheist", "non_atheist"), n, replace = TRUE, prob = c(p, 1-p))
  p_hats[i] <- sum(samp == "atheist")/n
}

hist(p_hats, main = "p = 0.02, n = 400", xlim = c(0, 0.18))
```

#### 10:


* * *

## On your own

#### 1:

#### 2:

#### 3:

