---
title: "Lab 5"
author: '[Team Mack and Jill]'
date: '[10/23/2017]'
output:
  html_document:
    fig_height: 4
    fig_width: 6
  pdf_document: default
---

**Author:** [Mackenzie O'Brien]

**Discussants:** [Jillian Preece]

* * *

**Load data:**


```{r echo=FALSE}
load(url("http://www.openintro.org/stat/data/mlb11.RData"))
```

* * *

#### 1:
The relationship is somewhat linear, with a .611 correlation value. I would feel hesitant to use a linear model; if I knew a team's at bats, I could estimate, but probably not correctly predict the number of runs.
```{r}

plot(mlb11$at_bats~mlb11$runs)
cor(mlb11$at_bats,mlb11$runs)
```


#### 2:
 Looking at the plot, there is a correlation between the number of at bats and runs; the more at bats, the more often there are also a lot of runs. However, there are outliers in the plot, where there were a small number of at bats but still a lot of runs and vice versa. The correlation is at 61% positive, which is moderate in strength.
```{r}
plot_ss(x=mlb11$at_bats, y=mlb11$runs, showSquares = TRUE)

```


#### 3: 
The smallest sum of squares that we got was 128026.6
```{r}
m1 <- lm(runs ~ at_bats, data = mlb11)
summary(m1)
```

#### 4:
The formula is y= -85.15663 + 0.34154*runs. The slope tells us that the number of home runs increases by 0.34 for every run. The more a team scores, the more likely there are to have home runs as well, which increases their chances of winning.
```{r}
m2<-lm(homeruns~runs, data = mlb11)
summary(m2)
```

#### 5:
He would predict around 700 runs based on the linear model, which is an overestimate by about 25 runs
```{r}
plot(mlb11$runs ~ mlb11$at_bats)
abline(m1)
```

#### 6:
There doesn't seem to be any pattern in the residuals, which means that the number of at bats does not significantly effect the number of runs.
```{r}
plot(m1$residuals ~ mlb11$at_bats)
abline(h = 0, lty = 3)  # adds a horizontal dashed line at y = 0
```

#### 7:
The normal probability plot suggests that the data is nearly normal, and the histogram is close, but suggests that it is less normal.
```{r}
hist(m1$residuals)
qqnorm(m1$residuals)
qqline(m1$residuals)  # adds diagonal line to the normal prob plot
```

#### 8:


* * *

## On your own

#### 1:

#### 2:

#### 3:

#### 4:

#### 5:

#### 6: